\include{config}
\begin{document}


\newcommand{\questionBox}[5]{
\noindent
 \fcolorbox{#1}{#2}{
 \begin{minipage}[l][12.6cm][c]{
 \dimexpr18cm-4
 \fboxsep-2
 \fboxrule}

 \fboxrule=.5mm
   \section*{#3 \hspace{\fill} Group Nr: \fcolorbox{black}{white}{\begin{minipage}[l][.6cm][c]{
   \dimexpr2cm-4
   \fboxsep-2
   \fboxrule}
   \hspace{\fill}
   \end{minipage}}}
   #4\\[1pc]
   Guidance questions:
   #5
   Description:\\
   \fcolorbox{black}{white}{\begin{minipage}[l][5.5cm][c]{
   \dimexpr17.3cm-4
   \fboxsep-2
   \fboxrule}
   \hspace{\fill}

   \fboxrule=2mm
   \end{minipage}
   }
   \end{minipage}
  }
  \\[2pc]
}





\questionBox{RealityBlue}{RealityBlue}{Reality}{Domain \fcolorbox{black}{white}{\begin{minipage}[l][.6cm][c]{
\dimexpr14cm-4
\fboxsep-2
\fboxrule}
\hspace{\fill}
\end{minipage}
}}{%
\begin{itemize}
  \item What is the privacy problem to be dealt with?
  \item What factors does the problem include? People, object, organizations?
  \item Is there a particular scenario you have in mind?
\end{itemize}
}
%
\questionBox{MeaningYellow}{MeaningYellow}{Meaning}{\hspace{\fill}}{%
\begin{itemize}
  \item What problem will the player be made aware of?
  \item How can one raise the awareness of the player?
  \item How can one change the player's attitude?
\end{itemize}
}
%
%
\questionBox{PlayGreen}{PlayGreen}{Play}{Genre  \fcolorbox{black}{white}{\begin{minipage}[l][.6cm][c]{
\dimexpr14cm-4
\fboxsep-2
\fboxrule}
\hspace{\fill}
\end{minipage}
}}{%
\begin{itemize}
  \item What is the games relation to privacy?
  \item What are the \textbf{goals}, \textbf{rules}, and \textbf{story} of the game?
\end{itemize}
}
%
\questionBox{TechnologyRed}{TechnologyRed}{Technolgy}{Medium  \fcolorbox{black}{white}{\begin{minipage}[l][.6cm][c]{
\dimexpr14cm-4
\fboxsep-2
\fboxrule}
\hspace{\fill}
\end{minipage}
}}{%
\begin{itemize}
  \item How will the player interact with the game?
  \item What are the advantages of creating a game for this technology?
  \item What are the limitations of creating a game for this technology?
\end{itemize}
}


\end{document}
